Single-fluorophore orientation determination with multiview polarized illumination: modeling and microscope design

### 2017-09-18 paper/paper/paper.tex
Patrick's funding sources.
Add Hari's funding.
Rudolf and Talon's paper edits re: our results compared to Fourkas

\textbf{Polarized illumination or detection} techniques vary the polarization of
light in the illumination or detection paths and exploit the anisotropic
absorption and emission patterns of single molecules to estimate their
orientation. By illuminating and detecting from the focal plane, not just the
focal point, these techniques can estimate the orientation of many molecules in
parallel without scanning. These techniques are easy to implement---changing the
illumination or detection polarization is simple with a polarization splitter
\cite{mehta2016} or universal compensator/polarizer \cite{shribak2003}---and the
reconstruction methods are straightforward \cite{fourkas2001, mehta2016,
  backer2016}. Also, these techniques keep the signal from a single molecule
localized on the detector, so they have a signal-to-noise ratio advantage over
defocusing and phase masking techniques. The main drawback is that these
techniques require several intensity measurements under different polarization
orientations to estimate the orientation of a single molecule. Despite the
requirement for multiple measurements, polarized illumination or detection
methods are good choices for live cell imaging because of their combination of
speed and ease of implementation.

To develop a polarized illumination or detection technique we need to choose a
method for varying the polarization and place it in the illumination or
detection path. The simplest and most inexpensive way to vary the polarization
is with a division-of-time (DoT) polarizer using a rotating polarizer or a
universal compensator/polarizer. Other polarization methods
(divison-of-amplitude, division-of-focal-plane) are more expensive and require
additional alignment or interpolation \cite{tyo2006}. The simplicity of DoT
polarization comes at the expense of temporal resolution---intensity
measurements are made one after the other which increases the acquisition
time. If we place the DoT polarizer in the detection path, we will block
valuable photons from reaching the detector which leads to unnecessary exposure
to the sample \cite{demay2011}. By placing the DoT polarizer in the illumination
arm we minimize exposure to the sample. We focus on DoT polarized illumination
in this paper because of its combination of simplicity and low sample exposure.

All single molecule orientation determination methods suffer from some degree of
anisotropic orientation uncertainty, i.e., some molecular orientations cannot be
determined as precisely as others. In some cases the orientation cannot be
determined at all---the forward model can be degenerate for specific dipole
orientations \cite{fourkas2001, lu2008}. We feel that the importance of
isotropic orientation uncertainty has been underappreciated. To our knowledge,
the only authors who have considered anisotropic orientation uncertainty have
only analyzed a subset of molecular orientations \cite{agrawal2012}. Our view is
that an ideal technique for determining the orientation of single molecules can
reconstruct the orientation with a small and nearly uniform uncertainty for all
molecule orientations.

@@

We consider a single molecule with a fixed absorption dipole moment
$\hat{\bs{\mu}}_{\text{abs}}$ that we express in spherical coordinates $\Theta$
and $\Phi$ (see Figure \ref{fig:coordinates}a)) as
\begin{align}
  \hat{\bs{\mu}}_{\text{abs}}(\Theta, \Phi) = \sin\Theta\cos\Phi\hat{\mb{x}} + \sin\Theta\sin\Phi\hat{\mb{y}} + \cos\Theta\hat{\mb{z}} \label{eq:mu}.
\end{align}
We place the molecule in the focal plane of an ideal, aplanatic,
polarization-preserving objective lens with its optical axis aligned with the
$\mh{z}$ axis. Next, we place a polarizer in the aperture plane with a variable
transmission axis $\hat{\mb{p}}_{\text{exc}}$ that we express as
\begin{align}
 \hat{\mb{p}}_{\text{exc}}(\phi_{\text{exc}}) = \cos\phi_{\text{exc}}\hat{\mb{x}} +
\sin\phi_{\text{exc}}\hat{\mb{y}},\label{eq:excfield}
\end{align}
where $\phi_{\text{exc}}$ is the angle between the transmission axis of the
polarizer and the positive $\mh{x}$ axis (see Figure
\ref{fig:coordinates}b)). Finally, we place a spatially incoherent and spatially
uniform light source (or its image) in the aperture plane to illuminate the
focal plane. In this geometry each point in the sample is illuminated by a range
of angles that can be changed by adjusting the radius of the stop in the
aperture plane. We denote the set of illuminated angles by $\Omega$ (see Figure
\ref{fig:coordinates}d)). If we use unit vectors $\hat{\mb{r}}$ expressed in
spherical coordinates $\theta$ and $\phi$ (see Figure \ref{fig:coordinates}c))
as
  \begin{align}
   \hat{\mb{r}}(\theta, \phi) = \sin\theta\cos\phi\hat{\mb{x}} + \sin\theta\sin\phi\hat{\mb{y}} + \cos\theta\hat{\mb{z}}, 
  \end{align}
  then the set of angles $\Omega$ can be expressed as
  \begin{align}
  \Omega = \{\phi, \theta\ |\ 0 < \phi \leq 2\pi, 0 < \theta \leq \alpha\},
  \end{align}
  where $\alpha$ is the angle between the optical axis and the most oblique
  illuminating ray. Equivalently, $\alpha$ can be expressed in terms of NA using
  \begin{align}
    \text{NA} = n\sin\alpha, 
  \end{align}
  where $n$ is the index of refraction of the sample medium. Note that the NA of
  the objective is always greater than or equal to the illumination NA because
  we can underfill the aperture plane.

@@

\subsection{Detection Efficiency}\label{detection}
Fourkas calculated the detection efficiency of a single molecule when an ideal
objective with its optical axis aligned with the $\mh{z}$ axis is focused on the
molecule and a polarizer is placed in the aperture plane\cite{fourkas2001}. We
use his expressions to calculate the detection efficiency without a polarizer as
\begin{align}
  \eta_{\text{det}} = 2(A + B\sin^2\Theta). \label{eq:scalardet}
\end{align}
The detection efficiency only depends on $\Theta$, not $\Phi$, because there is
no detection polarizer. We have assumed that the absorption dipole moment is
equal to the emission dipole moment.

Note that $A$ and $B$ in equation \ref{eq:coefficients} are a factor of
$\frac{3}{2}$ larger than the expressions given by Fourkas. We found that
Fourkas' expressions were incorrectly normalized (the limit of
$\eta_{\text{det}}$ as $\alpha\rightarrow \frac{\pi}{2}$ should be $\frac{1}{2}$), and
the extra factor of $\frac{3}{2}$ corrects the error. This correction does not
affect Fourkas' orientation reconstruction, but it does mean that Fourkas'
algorithm underpredicts the total emitted intensity by a factor of
$\frac{3}{2}$.

@@

\subsection{Intensity Measurements}\label{forward}
The detected intensity is proportional to the product of the sample exposure
$I_{\text{exp}}$, the absorption efficiency, and the detection efficiency
\begin{align}
  I \propto I_{\text{exp}}\eta_{\text{abs}}\eta_{\text{det}}\label{eq:forward_frame},
\end{align}
where the proportionality depends on the exposure time, the molecular quantum
efficiencies, and other constant factors. Equation \ref{eq:forward_frame} is the
forward model for a single intensity measurement. Figure \ref{fig:single-frame}
shows the efficiencies in three representative geometries. Note that in all
cases there are multiple orientations that give the same intensity
measurement. This means that a single intensity measurement does not give us
enough information to reconstruct the orientation of a single molecule. Next, we
will consider combining several intensity measurements to create polarized
illumination microscopes that can reconstruct the orientation of single
molecules.

@@

CRLBs and the associated area of uncertainty are parametrization dependent,
i.e., if we choose a different coordinate system these metrics will change. We
would like to compare microscope designs without choosing a parametrization, so
instead we use
\begin{align}
  \sigma_{\Omega} &\equiv \sin\Theta\sqrt{\text{det}\{\mb{F}^{-1}\}}
\end{align}
as our evaluation metric. We calculate the determinant of the inverse Fisher
information matrix---a parametrization-independent value called the
\emph{generalized variance} \cite{anderson1958}---take the square root, then
multiply by the Jacobian determinant, $\sin\Theta$. We call $\sigma_{\Omega}$
the \emph{solid-angle uncertainty} because it has units of steradians and is a
parametrization independent measure of the orientation uncertainty.

@@

To compare microscopes with different numbers of intensity measurements fairly,
we kept the total exposure to the sample constant by choosing
$I_{\text{exp}} = \frac{4000}{N}$. Note that $I_{\text{exp}}$ is a measure of
exposure to the sample, not the detected intensity or the total intensity
emitted by the molecule.

@@

\section{Results}\label{results}
Figure \ref{fig:single-arm} shows our results for single-view designs where a
single objective is used for illumination and detection. We swept through the
illumination and detection NA while keeping the sample exposure constant, and we
found that the lowest median and MAD of the solid-angle uncertainty occurs with
a small illumination NA and a large detection NA where
$\alpha \approx 65^{\circ}$ (see Figure \ref{fig:single-arm}e) at
NA${}_{\text{det}} \approx 1.2$). A small illumination NA maximizes the range of
absorption efficiencies, while a large detection NA optimizes the number of
detected photons and the range of the detection efficiencies. The optimal
detection NA is slightly larger than $\alpha = 57.4^{\circ}$ because increasing
the detection NA reduces the effect of shot noise. Note the relative importance
of illumination and detection NAs---reducing the illumination NA (an inexpensive
modification requiring underfilling the aperture plane) improves the solid-angle
uncertainty much less than increasing the detection NA (an expensive
modification requiring a higher-NA objective). Also note in Figure
\ref{fig:single-arm}c) that single-view designs suffer from high orientation
uncertainty when the molecules are oriented along the optical axis (the
molecules are not efficiently excited or detected), near the transverse plane
(it is ambiguous whether the molecule is oriented above or below the transverse
plane, see Figure \ref{fig:single-arm}b)), and near the polarizer orientations
(it is ambiguous whether the molecule is on either side of the polarizer
orientation, see Figure \ref{fig:single-arm}b)).

@@

Figure \ref{fig:asymmetric-double} shows our results for dual-view asymmetric
light-sheet illumination designs. We used light-sheet illumination on both sides
and kept the objectives orthogonal so that the light sheet from one objective
illuminates the focal plane of the other objective. Then, we swept through the
NA of one objective while maximizing the NA of the other objective so that both
objectives would touch the cover slip and each other
($\alpha_1 + \alpha_2 = 90^{\circ}$ in Figure \ref{fig:asymmetric-double}a)). We
swept through the NA asymmetry and the sample-exposure asymmetry while keeping
the total sample exposure constant, and found that symmetric designs are at a
local minimum of the median and MAD of the solid-angle uncertainty. We also
found that at extreme asymmetries where the exposure from the low-NA arm is much
larger than the exposure from the high-NA arm (top-left and bottom-right corners
of Figures \ref{fig:asymmetric-double}d) and e)) the median and MAD are
comparable to the symmetric light-sheet microscope. This means that if a very
high-NA objective is available and a low-NA objective can provide light sheet
illumination, this microscope will perform comparably with a dual-view
microscope with two medium-NA objectives. Note that this asymmetric exposure
configuration maximizes the use of the high-NA detection objective---if a
high-NA objective is available it should be used for detection as much as
possible. Figure \ref{fig:asymmetric-double} also shows that designs with
slightly asymmetric NA can trade off a low solid-angle uncertainty median for a
low solid-angle uncertainty MAD by changing the sample exposure ratio.

@@

Our results are limited in several ways. First, we only consider single
molecules in homogeneous environments. We ignore light reflected from the cover
slip and any other inhomogeneities in the sample. If we considered light
reflected from the cover slip we expect that the results would put a lower
weighting on large detection NAs because we would collect more light. Second, we
only considered ideal, aplanatic, polarization-preserving objectives. In
practice, these conditions are not always satisfied and the power from high-NA
rays is apodized by a factor of $\frac{n}{\cos\Theta}$
\cite{nov2006}. Therefore, our results are most accurate for low-NA rays and get
progressively worse for high-NA rays, although our major conclusions would not
change if we included this apodization factor. The main advantage of ignoring
apodization is the tractability of the problem---we have provided approximate
closed-form solutions for the illumination and detection efficiencies that have
allowed us to draw useful design conclusions. Third, we have used a Poisson
noise model which ignores noise introduced by the detector. Detector noise can
be a large fraction of the total noise at low intensities, so including detector
noise would increase the informational value of high intensity
measurements. Therefore, we expect that including the effects of detector noise
would favor microscopes with a large detection NA. Finally, we have focused on
the task of estimating the orientation of molecules and ignored the equally
important task of estimating their location. The task of jointly estimating the
orientation and location of single molecules from multiple views is a topic for
future work.

To compare the microscopes in this paper we used a fixed sample exposure. We
think that this is the fairest way to compare microscopes with different numbers
of intensity measurements. However, in cases where sample exposure and time are
not an issue it may be more useful to compare microscopes with the same total
detection exposure per measurement. This comparison would favor microscopes with
many intensity measurements even more that the results in this paper because
equal detection exposure would improve photon counting statistics.

We have considered single- and dual-view microscopes in a variety of cases, but
more multiview microscopes can be analyzed with the framework we have
developed. Wu et. al. have developed a three-view design with a third objective
below the cover slip\cite{wu2016}. Light-field detection schemes are also a type
of multiview microscope\cite{levoy2006}, and we plan to extend our analysis to
this case in future work.

@@

\section*{Funding}
TC was supported by a University of Chicago Biological Sciences Division
Graduate Fellowship. SM and RO were supported by NIH grant R01GM114274. HS was
supported by the Intramural Research Programs of the National Institute of
Biomedical Imaging and Bioengineering.

>>>>

\textbf{Polarized illumination or detection} techniques vary the polarization of
light in the illumination or detection paths and exploit the anisotropic
absorption and emission patterns of single molecules to estimate their
orientation. By illuminating and detecting from the focal plane, not just the
focal point, these techniques can estimate the orientation of many molecules in
parallel without scanning. These techniques are easy to implement---changing the
illumination or detection polarization is simple with a polarization splitter
\cite{mehta2016} or universal compensator/polarizer \cite{shribak2003}---and the
reconstruction methods are straightforward \cite{fourkas2001, mehta2016,
  backer2016}. Also, these techniques keep the signal from a single molecule
localized on the detector, so they have a signal-to-noise ratio advantage over
defocusing and phase masking techniques. The main drawback is that these
techniques require several intensity measurements under different polarization
orientations to estimate the orientation of a single molecule. Despite the
requirement for multiple measurements, polarized illumination or detection
methods are good choices for live-cell imaging because of their combination of
speed and ease of implementation.

To develop a polarized illumination or detection technique we need to choose a
method for varying the polarization and place it in the illumination or
detection path. The simplest and most inexpensive way to vary the polarization
is with a division-of-time (DoT) polarizer using a rotating polarizer or a
universal compensator/polarizer. Other polarization methods
(division-of-amplitude, division-of-focal-plane) are more expensive and require
additional alignment or interpolation \cite{tyo2006}. The simplicity of DoT
polarization comes at the expense of temporal resolution---intensity
measurements are made one after the other which increases the acquisition
time. If we place the DoT polarizer in the detection path, we will block
valuable photons from reaching the detector which leads to unnecessary exposure
to the sample \cite{demay2011}. By placing the DoT polarizer in the illumination
arm we minimize exposure to the sample. We focus on DoT polarized illumination
in this paper because of its combination of simplicity and low sample exposure.

All single molecule orientation determination methods suffer from some degree of
anisotropic orientation uncertainty, i.e., some molecular orientations cannot be
determined as precisely as others. In some cases the orientation cannot be
determined at all---the forward model can be degenerate for specific dipole
orientations \cite{fourkas2001, lu2008}. We feel that the importance of
isotropic orientation uncertainty has been underappreciated. To our knowledge,
the only authors who have considered anisotropic orientation uncertainty in 3D
have only analyzed a subset of molecular orientations \cite{agrawal2012}. Our
view is that an ideal technique for determining the orientation of single
molecules can reconstruct the orientation with a small and nearly uniform
uncertainty for all molecular orientations.

@@

We consider a single molecule with a fixed absorption dipole moment
$\hat{\bs{\mu}}_{\text{abs}}$ that we express in spherical coordinates $\Theta$
and $\Phi$ (see Figure \ref{fig:coordinates}a)) as
\begin{align}
  \hat{\bs{\mu}}_{\text{abs}}(\Theta, \Phi) = \sin\Theta\cos\Phi\hat{\mb{x}} + \sin\Theta\sin\Phi\hat{\mb{y}} + \cos\Theta\hat{\mb{z}} \label{eq:mu}.
\end{align}
We place the molecule in the focal plane of an ideal, aplanatic,
polarization-preserving objective lens with its optical axis aligned with the
$\mh{z}$ axis. Next, we place a polarizer in the aperture plane with a variable
transmission axis $\hat{\mb{p}}_{\text{exc}}$ that we express as
\begin{align}
 \hat{\mb{p}}_{\text{exc}}(\phi_{\text{exc}}) = \cos\phi_{\text{exc}}\hat{\mb{x}} +
\sin\phi_{\text{exc}}\hat{\mb{y}},\label{eq:excfield}
\end{align}
where $\phi_{\text{exc}}$ is the angle between the transmission axis of the
polarizer and the positive $\mh{x}$ axis (see Figure
\ref{fig:coordinates}b)). Finally, we place a spatially incoherent and spatially
uniform light source (or its image) in the aperture plane to illuminate the
focal plane. In this geometry each point in the sample is illuminated by a range
of angles that can be changed by adjusting the radius of the diaphragm in the
aperture plane. We denote the set of illuminated angles by $\Omega$ (see Figure
\ref{fig:coordinates}d)). If we use unit vectors $\hat{\mb{r}}$ expressed in
spherical coordinates $\theta$ and $\phi$ (see Figure \ref{fig:coordinates}c))
as
  \begin{align}
   \hat{\mb{r}}(\theta, \phi) = \sin\theta\cos\phi\hat{\mb{x}} + \sin\theta\sin\phi\hat{\mb{y}} + \cos\theta\hat{\mb{z}}, 
  \end{align}
  then the set of angles $\Omega$ can be expressed as
  \begin{align}
  \Omega = \{\phi, \theta\ |\ 0 < \phi \leq 2\pi, 0 < \theta \leq \alpha\},
  \end{align}
  where $\alpha$ is the angle between the optical axis and the most oblique
  illuminating ray. Equivalently, $\alpha$ can be expressed in terms of NA using
  \begin{align}
    \text{NA} = n\sin\alpha, 
  \end{align}
  where $n$ is the index of refraction of the sample medium. Note that the NA of
  the objective is always greater than or equal to the illumination NA because
  we can underfill the aperture plane.

@@

\subsection{Detection Efficiency}\label{detection}
In this section we will calculate the \emph{detection efficiency}---the fraction
of the power emitted by a single molecule that we detect. Fourkas calculated the
detection efficiency when an ideal objective with its optical axis aligned with
the $\mh{z}$ axis is focused on a single molecule and a polarizer is placed in
the aperture plane \cite{fourkas2001}. He found that
\begin{align}
  \eta_{\text{det}}^{\text{pol}} = A + B\sin^2\Theta + C\sin^{2}{\Theta} \cos{[2 (\Phi - \phi_{\text{det}}})], \label{eq:det_pol}
\end{align}
where $\phi_{\text{det}}$ is the angle between the transmission axis of the
detection polarizer and the positive $\mh{x}$ axis.

To calculate the detection efficiency without a polarizer, we use Equation
\ref{eq:det_pol} and take the sum of polarized detection efficiencies with
orthogonal polarizer orientations to find
\begin{align}
  \eta_{\text{det}} = 2(A + B\sin^2\Theta). \label{eq:scalardet}
\end{align}
In this case the detection efficiency only depends on $\Theta$, not $\Phi$,
because there is no detection polarizer. We have assumed that the absorption
dipole moment is equal to the emission dipole moment.

Note that $A$, $B$, and $C$ in equation \ref{eq:coefficients} are a factor of
$\frac{3}{2}$ larger than the expressions given by Fourkas. We found that
Fourkas' expressions were incorrectly normalized (the limit of
$\eta_{\text{det}}$ as $\alpha\rightarrow \frac{\pi}{2}$ should be $\frac{1}{2}$), and
the extra factor of $\frac{3}{2}$ corrects the error. This correction does not
affect Fourkas' orientation reconstruction, but it does mean that Fourkas'
algorithm underpredicts the total emitted intensity by a factor of
$\frac{3}{2}$.

@@

\subsection{Intensity Measurements}\label{forward}
The detected intensity is proportional to the product of the sample irradiance
$I_{\text{in}}$, the absorption efficiency, and the detection efficiency
\begin{align}
  I \propto I_{\text{in}}\eta_{\text{abs}}\eta_{\text{det}}\label{eq:forward_frame},
\end{align}
where the proportionality depends on the exposure time, the molecular quantum
efficiencies, and other constant factors. Equation \ref{eq:forward_frame} is the
forward model for a single intensity measurement. Figure \ref{fig:single-frame}
shows the efficiencies in three representative geometries. Note that in all
cases there are multiple orientations that give the same intensity
measurement. This means that a single intensity measurement does not give us
enough information to reconstruct the orientation of a single molecule. Next, we
will consider combining several intensity measurements to create polarized
illumination microscopes that can reconstruct the orientation of single
molecules.

@@

CRLBs and the associated area of uncertainty are parameterization dependent,
i.e., if we choose a different coordinate system these metrics will change. We
would like to compare microscope designs without choosing a parameterization, so
instead we use
\begin{align}
  \sigma_{\Omega} &\equiv \sin\Theta\sqrt{\text{det}\{\mb{F}^{-1}\}}
\end{align}
as our evaluation metric. We calculate the determinant of the inverse Fisher
information matrix---a parameterization-independent value called the
\emph{generalized variance} \cite{anderson1958}---take the square root, then
multiply by the Jacobian determinant, $\sin\Theta$. We call $\sigma_{\Omega}$
the \emph{solid-angle uncertainty} because it has units of steradians and is a
parameterization independent measure of the orientation uncertainty.

@@

To compare microscopes with different numbers of intensity measurements fairly,
we kept the irradiance incident on the sample constant by choosing
$I_{\text{in}} = \frac{4000}{N}$. Note that $I_{\text{in}}$ is a measure of
irradiance to the sample, not the detected intensity or the total intensity
emitted by the molecule.

@@

\section{Results}\label{results}
Figure \ref{fig:single-arm} shows our results for single-view designs where a
single objective is used for illumination and detection. We swept through the
illumination and detection NA while keeping the sample irradiance constant, and
we found that the lowest median and MAD of the solid-angle uncertainty occurs
with a small illumination NA and a large detection NA where
$\alpha \approx 65^{\circ}$ (see Figure \ref{fig:single-arm}e) at
NA${}_{\text{det}} \approx 1.2$). A small illumination NA maximizes the range of
absorption efficiencies, while a large detection NA optimizes the number of
detected photons and the range of the detection efficiencies. The optimal
detection NA is slightly larger than $\alpha = 57.4^{\circ}$ because increasing
the detection NA reduces the effect of shot noise. Note the relative importance
of illumination and detection NAs---reducing the illumination NA (an inexpensive
modification requiring underfilling the aperture plane) improves the solid-angle
uncertainty much less than increasing the detection NA (an expensive
modification requiring a higher-NA objective). Also note in Figure
\ref{fig:single-arm}c) that single-view designs suffer from high orientation
uncertainty when the molecules are oriented along the optical axis (the
molecules are not efficiently excited or detected), near the transverse plane
(it is ambiguous whether the molecule is oriented above or below the transverse
plane, see Figure \ref{fig:single-arm}b)), and near the polarizer orientations
(it is ambiguous whether the molecule is on either side of the polarizer
orientation, see Figure \ref{fig:single-arm}b)).

@@

Figure \ref{fig:asymmetric-double} shows our results for dual-view asymmetric
light-sheet illumination designs. We used light-sheet illumination on both sides
and kept the objectives orthogonal so that the light sheet from one objective
illuminates the focal plane of the other objective. Then, we swept through the
NA of one objective while maximizing the NA of the other objective so that both
objectives would touch the cover slip and each other
($\alpha_1 + \alpha_2 = 90^{\circ}$ in Figure \ref{fig:asymmetric-double}a)). We
swept through the NA asymmetry and the sample-exposure asymmetry while keeping
the total sample irradiance constant, and found that symmetric designs are at a
local minimum of the median and MAD of the solid-angle uncertainty. We also
found that at extreme asymmetries where the exposure from the low-NA arm is much
larger than the exposure from the high-NA arm (top-left and bottom-right corners
of Figures \ref{fig:asymmetric-double}d) and e)) the median and MAD are
comparable to the symmetric light-sheet microscope. This means that if a very
high-NA objective is available and a low-NA objective can provide light sheet
illumination, this microscope will perform comparably with a dual-view
microscope with two medium-NA objectives. Note that this asymmetric exposure
configuration maximizes the use of the high-NA detection objective---if a
high-NA objective is available it should be used for detection as much as
possible. Figure \ref{fig:asymmetric-double} also shows that designs with
slightly asymmetric NA can trade off a low solid-angle uncertainty median for a
low solid-angle uncertainty MAD by changing the sample exposure ratio.

@@

Our results are limited in several ways. First, we only consider single
molecules in homogeneous environments whose absorption and emission dipoles are
parallel. We ignore light reflected from the cover slip and any other
inhomogeneities in the sample. If we considered light reflected from the cover
slip we expect that the results would put a lower weighting on large detection
NAs because we would collect more light. Second, we only considered ideal,
aplanatic, polarization-preserving objectives. In practice, these conditions are
not always satisfied. For example, the power from high-NA rays is usually
apodized by a factor of $\frac{n}{\cos\Theta}$ \cite{nov2006}. Therefore, our
results are most accurate for paraxial rays and get progressively worse for
non-paraxial rays, although our major conclusions would not change if we
included this apodization factor. The main advantage of ignoring apodization is
the tractability of the problem---we have provided approximate closed-form
solutions for the illumination and detection efficiencies that have allowed us
to draw useful design conclusions. Third, we have used a Poisson noise model
which ignores noise introduced by the detector. Detector noise can be a large
fraction of the total noise at low intensities, so including detector noise
would increase the informational value of high intensity
measurements. Therefore, we expect that including the effects of detector noise
would favor microscopes with a large detection NA. Finally, we have focused on
the task of estimating the orientation of molecules and ignored the equally
important task of estimating their location. The task of jointly estimating the
orientation and location of single molecules from multiple views is a topic for
future work.

To compare the microscopes in this paper we used a fixed irradiance incident on
the sample. We think that this is the fairest way to compare microscopes with
different numbers of intensity measurements. However, in cases where sample
irradiance and time are not an issue it may be more useful to compare
microscopes with the same total detection irradiance per measurement. This
comparison would favor microscopes with many intensity measurements even more
that the results in this paper because equal detection irradiance would improve
photon counting statistics.

We have considered single- and dual-view microscopes in a variety of cases, but
other multiview microscopes can be analyzed with the framework we have
developed. Wu et. al. have developed a three-view design with a third objective
below the cover slip\cite{wu2016}. Light-field detection schemes are also a type
of multiview microscope\cite{levoy2006}, and we plan to extend our analysis to
this case in future work.

@@

\section*{Funding}
TC was supported by a University of Chicago Biological Sciences Division
Graduate Fellowship. SM and RO were supported by NIH grant R01GM114274. HS and
PL were supported by Marine Biological Laboratory Whitman Center Fellowships.
HS was supported by the Intramural Research Programs of the National Institute
of Biomedical Imaging and Bioengineering. PL was supported by NIH grant
R01EB017293.
